### 2025-07-19 getting-started.qmd
20250718 - updates

Functions are useful if you want to perform an operation multiple times.
Use of a function can save you time without needed to retype out all of the code each time.
For instance, let's say you want to convert temperature between Fahrenheit and Celsius, you could create a function to do that.

@@

@@

>>>>

@@

## If...Else Conditions {#sec-ifelse}

We can use the construction, `if()...else if()...else()` if we want to perform conditional operations.
The construction, `if()...else if()...else()` can only be used on one value at a time.

```{r}
player_rank <- 15

if(player_rank <= 10){ # check this condition first
  tier <- 1
  print(tier)
} else if(player_rank <= 20){ # if first condition was not met, check this condition next
  tier <- 2
  print(tier)
} else if(player_rank <= 30){ # if first two conditions were not met, check this condition next
  tier <- 3
  print(tier)
} else{ # if all other conditions were not met, then do this
  print("Don't draft this player!")
}
```

To apply conditional operations to a vector, we can use the `ifelse()` function.

```{r}
player_rank <- c(1, 10, 20, 40, 100)

tier <- ifelse(
  player_rank <= 10, # check this condition
  1, # assign this value if true
  2) # assign this value if false

tier
```

@@

Now, let's put together what we have learned to create a useful function.
Functions are useful if you want to perform an operation multiple times.
Any operation that you want to perform multiple times, you can create a function to accomplish.
Use of a function can save you time without needed to retype out all of the code each time.
For instance, let's say you want to convert temperature between Fahrenheit and Celsius, you could create a function to do that.
In this case, our function has two arguments: `temperature` (in degrees) and `unit` of the original temperature (`F` for Fahrenheit or `C` for Celsius, where the default unit is Fahrenheit).

### 2025-07-19 modern-portfolio-theory.qmd
20250701 - citations
20250708 - track chunk execution times
20250717 - chapter overviews
20250718 - updates

@@

@@

>>>>

This chapter provides an overview of modern portfolio theory.

@@

If the `maxreturnPortfolio()` function worked as expected, the following could should work for determining the portfolio with the maximum return at each of various risk levels.
However, there is a known bug in the `fportfolio` package [@R-fPortfolio] that the optimal portfolio (based on maximum returns) does not change when changing the target risk level, suggesting that it is not taking into account the target risk level specified by the user (see here: <https://stackoverflow.com/q/78784306/2029527>).

@@

Below, we use the `mvFrontier()` function from the `NMOF` package [@R-NMOF; @Gilli2019_packages; @Schumann20112024_packages] to compute the efficient frontier.
